---
title: "Bevers"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(dplyr)
library(purrr)
library(ggplot2)

knitr::opts_chunk$set(echo = TRUE)


```

## Introduction

Reynolds (1994) describes a small part of a study of the long-term temperature dynamics of beaver Castor canadensis in north-central Wisconsin. Body temperature was measured by telemetry every 10 minutes for four females, but data from a one period of less than a day for each of two animals is used there.

The vast majority of the text and code are taken from the `beavers` data documentation page.

```{r}

```

## Data description

In our processed data, we have combined data from the original `beaver1` and `beaver2`. The below table shows how many time observations for each beaver.

```{r}
# this table calculation should be loaded in the final report
bev_num_counts <- bevs |>
  dplyr::count(bev_num)
```

```{r}
# this table should be displayed in the report
bev_num_counts |>
  knitr::kable()
```

The main columns of our data are as follows:

-   `day`: Day of observation (in days since the beginning of 1990), December 12--13 (beaver1) and November 3--4 (beaver2).
-   `time`: Time of observation, in the form `0330` for 3:30am
-   `temp`: Measured body temperature in degrees Celsius
-   `activ`: Indicator of activity outside the retreat

Below we are counting the recoded `activ` column, `activ_char` by the `bev_num`

```{r}
# there is a table calculation here that ends up being displayed in the final report
activ_char_counts <- bevs |>
  dplyr::count(bev_num, activ_char)

activ_char_counts |>
  knitr::kable()
```

We also have a figure looking at temperatures of each beaver over time. The red points are when the beaver was active.

```{r}

```

## References

```{=html}
<!--
You do not need to turn this into a bibliography + citation
-->
```
P. S. Reynolds (1994) Time-series analyses of beaver body temperatures. Chapter 11 of Lange, N., Ryan, L., Billard, L., Brillinger, D., Conquest, L. and Greenhouse, J. eds (1994) Case Studies in Biometry. New York: John Wiley and Sons.
